A Bayesian networks approach to infer social changes from burials in northeastern Taiwan during the European colonization period

### 2021-08-24 analysis/paper/paper.Rmd
knit successfully after reordering the bgof2() and using lockfile pkgs by removing the updated ones

```{r figure-KWL-map, fig.cap = "The location of Kiwulan and the European forts at Heping dao and Tamsui in northern Taiwan (modified from Wang and Marwick, 2020). Map data from naturalearthdata.com."}

knitr::include_graphics(here::here("analysis", "figures", "000-KWL-map.png"))
```

@@

```{r custom-function, include=FALSE}
suppressWarnings(source(here::here("analysis", "code", "999-bgof-custom-function.R")))
```

>>>>

```{r figure-KWL-map, fig.cap = "The location of Kiwulan and the European forts at Heping dao and Tamsui in northern Taiwan (modified from Wang and Marwick, 2020). Map data from naturalearthdata.com."}
knitr::include_graphics(here::here("analysis", "figures", "000-KWL-map.png"))
```

@@
